SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-16 2019-ActaInformatica/ActaInformatica.tex
minor changes

\abstract{Open pNets are used to model the behaviour of open systems, both
synchronous and asynchronous, expressed in various process calculi or
languages. They are endowed with a symbolic operational semantics in
terms of open automata, which allows us to check properties of
such systems in a compositional manner. 
We implement an algorithm computing these semantics,
building predicates expressing the synchronization conditions
between the events of the pNet sub-systems. Checking such
predicates requires symbolic reasoning about first order logics and application-specific data. We use the Z3 SMT engine to check
satisfiability of the predicates.
%As an industrial oriented use-case, %we use so-called ``architectures''
%for BIP systems, that have been used in the framework of an ESA project and to specify the control software of a nanosatellite at the EPFL Space Engineering Center. 
As a use-case, we use pNets to encode a BIP architecture
extended with explicit data, and compute its
open automaton semantics. This automaton may be used to prove
behavioural properties such as safety and liveness.
\TODO{Add new contrib}
\todoMargin{Should we remove Min ?}
\keywords{pNets, software components, symbolic semantics, SMT}
}

@@

In the nineties, several 
works extended the basic behavioural models based on labelled
transition systems to formalize value-passing or parameterized systems, using
various symbolic encodings of the
transitions~\cite{deSimone85,Larsen87,HennessyLin:TCS95,Linconcur96}. 
In \cite{Linconcur96}, Lin considered value-passing calculi, for which he
developed a symbolic behavioural semantics, and proved algebraic properties.
Separately, Rathke~\cite{HennessyRathke:TCS98} defined another
symbolic semantics for 
a parameterized broadcast calculus, together with strong and weak bisimulation
equivalences, and developed a symbolic model-checker based on a tableau
method for these processes. Thirty years later, no
practical verification approach and no verification platform use this kind of approaches to provide proof methods for
value-passing processes or open process expressions.

>>>>

\abstract{Open pNets are formal models that can express the behaviour of open systems, either
synchronous, asynchronous, or heterogeneous. They are endowed with a symbolic operational semantics in
terms of open automata, which allows us to check properties of
such systems in a compositional manner. 
We propose and implement an algorithm computing these semantics,
building predicates expressing the synchronization conditions
between the events of the pNet sub-systems. Checking such
predicates requires symbolic reasoning about first order logics and application-specific data. We use the Z3 SMT engine to check
satisfiability of the predicates.
%As an industrial oriented use-case, %we use so-called ``architectures''
%for BIP systems, that have been used in the framework of an ESA project and to specify the control software of a nanosatellite at the EPFL Space Engineering Center. 
We also present several use-cases, in particular, encoding a BIP architecture
extended with explicit data and computing its
open automaton semantics. This automaton may be used to prove
behavioural properties such as safety and liveness.
\TODO{Add new contrib}
\todoMargin{Should we remove Min ?}
\keywords{pNets, software components, symbolic semantics, SMT}
}

@@

In the nineties, several 
works extended the basic behavioural models based on labelled
transition systems to formalize value-passing or parameterized systems, using
various symbolic encodings of the
transitions~\cite{deSimone85,Larsen87,HennessyLin:TCS95,Linconcur96}. 
In \cite{Linconcur96}, Lin considered value-passing CCS, for which he
developed a symbolic behavioural semantics, and developed algorithms for checking symbolic bisimulations.
Separately, Rathke~\cite{HennessyRathke:TCS98} defined another
symbolic semantics for 
a parameterized broadcast calculus, together with strong and weak bisimulation
equivalences, and developed a symbolic model-checker based on a tableau
method for these processes. 
Later on, symbolic semantics were extended to the $\pi$-calculus and decision algorithms for various symbolic bisimulations were proposed \cite{Li99,Deng2001}. However, no
practical verification approach or  platform uses this kind of approaches to provide proof methods for
value-passing processes or open process expressions.
